
\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{enumitem}

\title{The Entropy Ledger: A Resource Theory and Information Inequalities for Consistent Time Travel\\
\large (with Experimental Proposals and a Metaphysics Appendix)}
\author{Spiros Ts. \and Collaborators}
\date{\today}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{proposition}{Proposition}

\newcommand{\KL}{D_{\mathrm{KL}}}
\newcommand{\Ps}{p_{\mathrm{succ}}}

\begin{document}
\maketitle

\begin{abstract}
We develop a full \emph{resource theory for consistent time travel} and derive operational information inequalities that quantify the net information gain obtainable from retrocausal (postselected) channels. Our central results include a Loop Data-Processing Inequality (Loop-DPI), a single-shot strong converse, and a thermodynamic \emph{Entropy Ledger} that lower-bounds the heat dissipation needed to restore consistency (Novikov) as a Kullback--Leibler I-projection cost. We extend the theory to multi-loop networks, propose experimentally testable photonic and ion-trap protocols, and include a Metaphysics Appendix formalizing identity and free will as history-functionals consistent with the Ledger. We also outline realistic pathways to ``real'' time travel in the operational sense: relativistic time dilation (one-way to the future) and laboratory realizations of effective retrocausality via heralded postselection and entanglement-assisted protocols.
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_model_resource_theory}
\input{sections/03_loop_dpi_and_converse}
\input{sections/04_entropy_ledger}
\input{sections/05_multiloop_networks}
\input{sections/06_thermo_and_single_shot}
\input{sections/07_experiments_real_tt}
\input{sections/08_discussion_open}
\appendix
\input{sections/D_additional_figures}

\input{sections/C_detailed_proofs}

\input{sections/A_metaphysics_appendix}
\input{sections/B_notation_proofs_outline}

\bibliographystyle{plain}
\bibliography{refs}
% \begin{thebibliography}{9}
\bibitem{Landauer1961} R. Landauer. Irreversibility and heat generation in the computing process. \emph{IBM Journal of Research and Development}, 1961.
\bibitem{Crooks} G. E. Crooks. Entropy production fluctuation theorem and the nonequilibrium work relation for free energy differences. \emph{Phys. Rev. E}, 1999.
\bibitem{Jarzynski} C. Jarzynski. Nonequilibrium equality for free energy differences. \emph{Phys. Rev. Lett.}, 1997.
% \end{thebibliography}

\end{document}
