
\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{times}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{titlesec}
\usepackage{abstract}

\titleformat{\section}{\large\bfseries}{\thesection}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\title{\bfseries The Entropy Ledger: A Resource Theory and Information Inequalities for Consistent Time Travel}
\author[1]{Spiros Ts.}
\author[2]{Collaborators}
\affil[1]{Independent Researcher}
\affil[2]{Various Institutions}
\date{\vspace{-1em}}

\begin{document}
\twocolumn[
\maketitle
\begin{onecolabstract}
We develop a resource theory for consistent time travel with operational bounds (Loop-DPI), a thermodynamic Entropy Ledger (Novikov as I-projection), multi-loop network cut-sets, and single-shot strong converses. We propose photonic and ion-trap experiments and include a metaphysics appendix formalizing identity and free will as Ledger-compatible functionals.
\end{onecolabstract}
\vspace{1em}
]

\input{../tex/sections/01_introduction}
\input{../tex/sections/02_model_resource_theory}
\input{../tex/sections/03_loop_dpi_and_converse}
\input{../tex/sections/04_entropy_ledger}
\input{../tex/sections/05_multiloop_networks}
\input{../tex/sections/06_thermo_and_single_shot}
\input{../tex/sections/07_experiments_real_tt}
\input{../tex/sections/08_discussion_open}

\section*{Methods}
Key derivations and simulations are provided in the Appendices.

\section*{Data availability}
Simulation scripts are included in the repository.

\section*{Code availability}
All code to reproduce figures is provided.

\section*{References}
{\small
\begin{enumerate}
\item R. Landauer, IBM J. Res. Dev. (1961).
\item G. E. Crooks, Phys. Rev. E (1999).
\item C. Jarzynski, Phys. Rev. Lett. (1997).
\end{enumerate}
}

\appendix
\input{../tex/sections/C_detailed_proofs}
\input{../tex/sections/D_additional_figures}
\input{../tex/sections/A_metaphysics_appendix}
\input{../tex/sections/B_notation_proofs_outline}

\end{document}
