
\documentclass[aps,prl,twocolumn,10pt,superscriptaddress,longbibliography]{revtex4-2}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{bm}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\KL}{D_{\mathrm{KL}}}
\newcommand{\Ps}{p_{\mathrm{succ}}}

\begin{document}
\title{The Entropy Ledger: A Resource Theory and Information Inequalities for Consistent Time Travel}

\author{Spiros Ts.}
\affiliation{Independent Researcher}
\author{Collaborators}
\affiliation{Various Institutions}

\begin{abstract}
We develop a resource theory for consistent time travel with operational bounds (Loop-DPI), a thermodynamic Entropy Ledger (Novikov as I-projection), multi-loop network cut-sets, and single-shot strong converses. We propose photonic and ion-trap experiments and include a metaphysics appendix formalizing identity and free will as Ledger-compatible functionals.
\end{abstract}

\maketitle

% --- Main text brought in from the base sections directory ---
\input{../tex/sections/01_introduction}
\input{../tex/sections/02_model_resource_theory}
\input{../tex/sections/03_loop_dpi_and_converse}
\input{../tex/sections/04_entropy_ledger}
\input{../tex/sections/05_multiloop_networks}
\input{../tex/sections/06_thermo_and_single_shot}
\input{../tex/sections/07_experiments_real_tt}
\input{../tex/sections/08_discussion_open}

\appendix
\input{../tex/sections/C_detailed_proofs}
\input{../tex/sections/D_additional_figures}
\input{../tex/sections/A_metaphysics_appendix}
\input{../tex/sections/B_notation_proofs_outline}

\bibliographystyle{apsrev4-2}
\bibliography{../tex/refs}
% \begin{thebibliography}{99}
\bibitem{Landauer1961} R. Landauer, IBM J. Res. Dev. (1961).
\bibitem{Crooks} G. E. Crooks, Phys. Rev. E (1999).
\bibitem{Jarzynski} C. Jarzynski, Phys. Rev. Lett. (1997).
% \end{thebibliography}
\end{document}
