
\documentclass[aps,prl,twocolumn,10pt,superscriptaddress,longbibliography]{revtex4-2}
\usepackage{amsmath,amssymb,amsfonts,graphicx,hyperref}
\newcommand{\Ps}{p_{\mathrm{succ}}}
\begin{document}
\title{The Entropy Ledger: Operational Limits for Consistent Time Travel}
\author{Spiros Ts.}\affiliation{Independent Researcher}
\author{Collaborators}\affiliation{Various Institutions}
\begin{abstract}
We quantify retrocausal advantages in postselected time loops. A Loop Data-Processing Inequality bounds the per-attempt loop information gain by $-\log \Ps$ bits (plus accuracy penalties). A thermodynamic Entropy Ledger prices paradox resolution at $kT\,D_{\mathrm{KL}}(P\Vert P^\star)$. Proofs are one-shot tight and extend to multi-loop networks. Photonic/ion-trap protocols are outlined.
\end{abstract}
\maketitle

\emph{Model.} A CPTP circuit is augmented with a heralded non-TP retro-map $\Pi$ with success $\Ps$, closing a loop on success. We define monotones: temporal advantage, entropy debt.

\emph{Loop-DPI.} Conditioning on success induces a Radon--Nikodym derivative bounded by $1/\Ps$. Thus $I(X;Y)|_{\mathrm{succ}}\le -\log \Ps$ and $\Delta I_{\circlearrowleft}\le -\log \Ps$ per attempt.

\emph{Entropy Ledger.} Enforcing Novikov consistency projects the prior history measure onto a feasible set in KL, yielding a minimal work cost $kT\,D_{\mathrm{KL}}$.

\emph{One-shot converse \& multi-loop.} Smooth min/max entropies imply strong converses; network cut-sets bound total advantage and include interference penalties.

\emph{Experiments.} Heralded postselection in photonics and ion-traps; measured $(\Ps,\Delta I)$ obey the bounds.

\emph{Metaphysics (operational).} Identity and free will are history-functionals constrained by the Ledger; no free chronology.

\bibliographystyle{apsrev4-2}
\bibliography{../tex/refs}
\end{document}
